---
title: "Untitled"
author: "Tony Mei"
date: "9/10/2019"
output: html_document
---
```{r}
library(stringr)
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
```

```{r}
FL_names <- str_trim(sub("\\s\\w\\.|\\S\\w+\\.\\s","", name))
FL_names
FL_names1<-sub("(\\w+),\\s+(\\w+)","\\2 \\1", FL_names)
FL_names1

```

2. Construct a logical vector indicating whether a character has a title(ie., Rev. and Dr.)
```{r}
titled_name<-str_detect(name, "Rev.|Dr.")
titled_name
cbind(name, titled_name)
```

3.
```{r}
second_name <- str_detect(name, "[A-Z]\\.{1}")
second_name
cbind(name, second_name)
```


4.
a) 
[0-9]+\\$
```{r}
test<-c("12308129038asdas09$", "hello#", "233124$1", "1$")
number_vec<-unlist(str_extract_all(test, "[0-9]+\\$"))
number_vec
```
Matches string patterns that have 0-9 digits one or more times followed by the $ sign.

b) 
```{r}
test1<-"badb, abcedf, eheheh, badasdasdasd, abcd"
number_vec1<-unlist(str_extract_all(test1, "\\b[a-z]{1,4}\\b"))
number_vec1
```
Matches words that have one and four lowercase characters only.

c).*?\\.txt$
```{r}
test2<-c("homework.gif", "homework.jpg", "homework2.txt")
number_vec2<-unlist(str_extract_all(test2, ".*?\\.txt$"))
number_vec2
```
Matches strings that end with .txt
d)
\\d{2}/\\d{2}/\\d{4}
```{r}
test3<-c("07/17/1990", "ab/12/a123", "0909111")
number_vec3<-unlist(str_extract_all(test3, "\\d{2}/\\d{2}/\\d{4}"))
number_vec3
  
```

Matches string with a format of XX/XX/XXXX, X can only be digits.
e)
<(.+?)>.+?</\\1>
```{r}
test4<-c("<a>HEllo", "<a> Hello </a>", "<b>My name is</d>", "<html>Hi there</html>")
number_vec4<-unlist(str_extract_all(test4, "<(.+?)>.+?</\\1>"))
number_vec4
```
Matches the start tag, then characters in between and then end tag. The start tag and end tag must be the same letter.

9.
The following code hides a secret message. Crack it with R and regular expressions. Hint: Some of the characters are more revealing than others! The code snippet is also available in the materials at www.r-datacollection.com.

clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5 fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr

```{r}
code<-"clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5 fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
crack_code<-unlist(str_extract_all(code, "[[A-Z][:punct:]]"))
crack_code
```

